---
title: "mypopgen Package Vignette"
author: "Matthew Murray"
date: "`Sys.Date()`"
output: html_document
---

A vignette for the use of the mypopgen package. Illistrated with made up data. 

```{r setup, echo=FALSE}
my_seg_sites<-function(my_seqs){
	len<-dim(my_seqs)[1]
	sites<-vector()
	for (i in 2:len){
		sites<- c(sites,which(my_seqs[i,] != my_seqs[1,]))
	}
	return(unique(sort(sites)))
}

# calculate nucleotide diversity 
# all combinations method 
my_pi<- function(my_seqs){
	n=dim(my_seqs)[1]
	all_combs=as.data.frame(combn(seq(1,n),2))
	pis<-vector()
	for (i in 1:length(all_combs)){
		pis<- c(pis, 
		sum(my_seqs[all_combs[1,i],] !=my_seqs[all_combs[2,i],])/
			length(my_seqs[all_combs[i,2],]))
	}
	return(sum(pis))
}
```

Creating some data to play with. 

```{r}
bases<- c("A","T","C","G")
seq1 <- sample(bases,1000, replace=TRUE)
seqs<- as.data.frame(matrix(NA,nrow=9,ncol=1000))
seqs[1,]<-seq1
for ( i in 2:10){
snps<- sample(bases,3, replace=TRUE)
snp_pos<-sample(seq(1,1000),3)
seq2<- seq1
seq2[snp_pos]<-snps
seqs[i,]<-seq2
}
```
 Take a look at the theoretical 1 kb of sequence created
```{r Sequence}
seq1
```

Here is a snippit of multiple samples, somehting similar to a potential real dataset
```{r}
seqs[1:10,1:20]
```

Now we can find which sites in our kb or sequence using the "my_seg_sites" function
```{r my_seg_sites}
my_seg_sites(seqs)
```

Now if we pull out the positions that are segregating to take a look. We can see all of these sites have at least one snp. 
```{r, results='hold'}
sites<- my_seg_sites(seqs)
seqs[,sites]
```

Now we can take all of these sites and calculate nucleotide diversity using the "my_pi" funciton. 
```{r}
my_pi(seqs)
```








